% !TEX TS-program = xelatex
% !TEX encoding = UTF-8
% vim: tw=79

\documentclass[10pt,a4paper,parskip]{scrartcl}

\usepackage{geometry}
\geometry{tmargin=1in,bmargin=1in,lmargin=1.4in,rmargin=1.4in}

\usepackage[english]{babel}

% character encoding
\usepackage{fontspec}

\usepackage{xunicode}
\usepackage{xltxtra}

% spacing
\frenchspacing
\setlength{\parskip}{12pt}
\setlength{\parindent}{0pt}

\begin{document}

\begin{center} {\Large Contract} \end{center}

[ LOGO ]

[ ADDRESS ]

[ PHONE ]

[ CONTACT E-MAIL ]

[ DATE ]

\section{Summary:}

We will always do our best to fulfill your needs and meet your goals, but
sometimes it is best to have a few simple things written down so that we both
know what is what, who should do what and what happens if stuff goes wrong. In
this contract you won't find complicated legal terms or large passages of
unreadable text. We have no desire to trick you into signing something that you
might later regret. We do want what's best for the safety of both parties, now
and in the future.

\section{In short:}

You ([CLIENT COMPANY]) are hiring us ([MY COMPANY]) to [PROJECT NAME OR
DESCRIPTION] at the hourly rate of [HOURLY RATE] per hour. Of course it's a
little more complicated, but we'll get to that.

\section{What do both parties agree to do?}

As our customer, you have the power and ability to enter into this contract on
behalf of your company or organization. You agree to provide us with everything
that we need to complete the project including text, images and other
information as and when we need it, and in the format that we ask for. You
agree to review our work, provide feedback and sign-off approval in a timely
manner. Work will be deemed accepted if no feedback is given within 14 days.
Deadlines work two ways and you will also be bound by any dates that we
set together. You also agree to stick to the payment schedule set out at the
end of this contract.

We have the experience and ability to perform the services you need from us and
we will carry them out in a professional and timely manner. Along the way we
will endeavor to meet all the deadlines set but we can't be responsible for a
missed launch date or a deadline if you have been late in supplying materials
or have not approved or signed off our work on-time at any stage. On top of
this we will also maintain the confidentiality of any information that you give
us.

\section{Getting down to the nitty gritty}

\subsection{What we need from you}

Below is a list of items we’ll need up front from you. Every project is
slightly different, so there may be things we’ve missed from this list, but we
will let you know as soon as we’re able if we’ve forgotten something we need.

[LIST OF NEEDS] (includes credentials, access to any necessary services or
assets, etc)

\subsection{Browser Compatibility}

We have agreed to test our code in IE10+ as well as the latest releases of
Opera, Safari, and Chrome. Additionally we test on mobile Safari and mobile
Chrome (iOS devices, Android devices). If you need browsers other than those
listed tested, please provide us with a list of the browsers and devices.
Testing additional browsers requires more testing time as well as potentially
needing to code for that specific browser.
We code everything with progressive enhancement in mind. This means that modern
browsers may show slight differences to older browsers (such as text and box
shadows, rounded corners, etc) based on what a browser is able to render. Any
changes will not affect the user experience.

\subsection{Testing}

We write tests before we write our code, which allows us to make sure that all
required functionality is not only present, but works no matter how often we
change things around. If your employees or other contractors will be working on
the project along side us, we require that they also write tests for all code
they produce to make sure we are all on the same page and not stepping on each
others toes.

\subsection{Version Control}

Git allows us to keep track of all changes that happen in your application.
This way, if a bug is introduced we can quickly find where it was added and
roll back to the previous bug-free state while we fix things up! We require
code be under version control so we can work on your application with your
employees or other contractors without worrying that we may be undoing or
overwriting each others changes.

\subsection{Timeline}

This project is scheduled to begin [START DATE] and will last a [PROJECT DURATION].
Below is the milestone schedule:

[MILESTONE NAME, \# DAYS REQUIRED]
This contract will be declared complete when all work completed has been paid in full.

\subsection{Additional development}

Any additional development needed above and beyond what we have agreed to here
must be accompanied by an additional contract which we will be happy to provide
upon request. We retain the right to refuse additional work that is not
specifically outlined in this document.

\section{Contact}

All communications will be made during regular business hours (Monday-Friday,
9am-5pm CST, excluding holidays) and we will return any contact requests within
one business day unless we notify you ahead of time that we will be out of the
office. Of course we understand that emergencies do arise, so in the case of
one know that our hours will be billed at time and a half. We appreciate
communication in a text-based medium, but understand that not all discussions
are easily done this way. We’re happy to speak to you on the phone, over
Skype/Google Hangout, or in person if you are in the [MY CITY] area, keeping in
mind that any decisions that are made will be written down and require your
written approval.

As we value your time as well as our own, we ask that all meetings be scheduled
a minimum of two business days in advance and be accompanied by an agenda so
that we can be fully prepared. If we are unable to attend a meeting at your
suggested time, we will be happy to provide two times that will work for us.
Meetings must start and end on or before the time allotted and will be charged
for whether you attend or not.

\subsection{Project Management}

If you do not have a preferred project management tool, we will provide you
with a login for ours where you will be able to see the status of the project
down to the specific task, so you will always be kept up to date. We’ll be
relying on you to participate by answering our questions, stating your
approval, requesting changes, and verifying completeness through the tool as
well. We ask for a one business day turnaround time on responses so we can keep
things moving along at a pace that will allow us to hit the milestones we
decided on together. To keep the project organized and the management of it
easier, we prefer not to communicate any of the information stated above over
ordinary email.

\section{Legal stuff}

Although we test extensively, we can't guarantee that the functions contained
in any application will always be error-free and so we can't be liable to you
or any third party for damages, including lost profits, lost savings or other
incidental, consequential or special damages arising out of the operation of or
inability to operate this application and any other web pages, even if you have
advised us of the possibilities of such damages.

If any provision of this agreement shall be unlawful, void, or for any reason
unenforceable, then that provision shall be deemed severable from this
agreement and shall not affect the validity and enforceability of any remaining
provisions.

\section{Copyrights}

You guarantee to us that any elements of text, graphics, photos, designs,
trademarks, or other artwork that you provide us for inclusion in the
application are either owned by your good selves, or that you have permission
to use them.

When we receive your final payment, copyright is automatically assigned as
follows:

You own the graphics and other visual elements that we create for you for this
project. We will give you a copy of all files and you should store them safely
as we are not required to keep them or provide any native source files that we
used in making them.

You also own text content, photographs and other data you provided, unless
someone else owns them. We own the code we produced and we retain the rights to
license it how we choose or to contribute it back to the open source project
which it is based on.
We love to show off our work and share what we have learned with other people,
so we also reserve the right to display and link to your completed project as
part of our portfolio and to write about the project on web sites, in magazine
articles and in books as well as speak about them publicly at conferences. Of
course we’re happy to keep this information to ourselves until your project
goes live or 6 months from the handover date, whichever is sooner.

\section{Payments}

We are sure you understand how important it is as a small business that you pay
the invoices that we send you promptly.  As we're also sure you'll want to stay
friends, you agree to stick tightly to the following payment schedule.

\subsection{Payment Schedule}

We bill every other week on Friday and all invoices are payable upon receipt.

A deposit of [DEPOSIT AMOUNT] is due up front and will be subtracted from the
last invoice.
Any payments not received within 7 days will halt work until the payment is
received. If payment is late twice during the project, we retain the right to
ask for prepayment of hours or to end the project, whichever is deemed more
fitting for the situation.

If either party chooses to end the project, it must be done in writing. Please
keep in mind that the deposit will be forfeited and any work that has been paid
for up to that point will be turned over to you.

\section{But where is all the horrible small print?}

Just like a parking ticket, you cannot transfer this contract to anyone else
without our permission. This contract stays in place and need not be renewed.
If for some reason one part of this contract becomes invalid or unenforceable,
the remaining parts of it remain in place.

Although the language is simple, the intentions are serious and this contract
is a legal document under exclusive jurisdiction of [MY STATE] courts.


\vspace{1cm}

\noindent The undersigned agrees to the terms of this agreement on behalf of
his or her organization or business.\\\\

\noindent \begin{tabular}{l l l}
On behalf of the Client: & \rule{6cm}{.2pt}        & Date: \rule{2.4cm}{.2pt}\\
                         & [CLIENT REPRESENTATIVE] & \\\\\\
The Consultant:          & \rule{6cm}{.2pt}        & Date: \rule{2.4cm}{.2pt}\\
                         & [CONSULTANT NAME]       & \\
\end{tabular}

\end{document}
